DeepSphere: a graph-based spherical CNN

### 2019-11-14 main.tex
organize todos

\newcommand{\fix}{\marginpar{FIX}}
\newcommand{\new}{\marginpar{NEW}}
\newcommand{\todo}[1]{{\color[rgb]{.6,.1,.6}{#1}}}
\newcommand{\nati}[1]{{\color[rgb]{.3,.5,.9}{#1}}}
\newcommand{\mart}[1]{{\color[rgb]{.9,.5,.3}{#1}}}

@@

story: there are tradeoffs when designing a spherical CNN -> DS strikes a controllable balance between efficiency / cost and exactitude / equivariance
% DSv2 has a clear tradeoff between equivariance and computational cost

* method development: tool that solve a need (balance btw the desiderata: equiv vs cost)\\
* research question: anisotropy (highlight from the start or leave it as a dangling question in the end)\\

contributions:\\
* theory $\Rightarrow$ convergence (better graph)\\
* experiments on relevant problems (not spherical MNIST) $\Rightarrow$ check the desiderata\\
  * surprising: anisotropy doesn't seem useful\\

\todo{
\begin{itemize}
% 	\item shall we really name it? Or simply reference the general idea of a graph-based spherical CNN. [Yes]
% 	\item adjacency matrix: $A$ instead of $W$? nath: I am for W
% 	\item anonymize DeepSphere citation - Not doing that
% 	\item climate spherical figure: inputs with TC and AR labels superimposed [Frédérick]
	\item More details on related work? Not sure we have the space. If yes, detailed comparison with related work after method. \nati{I would drop this.}
	\item PSD of climate data: how does it compare to cosmo and 3D objects?
	\item align the spheres in figure 1
	\item mention that \citep{esteves2018sphericalcnn} and \citep{cohen2018sphericalcnn} computed equivariance error
	\item check footnotes
	\item climate data on spectrum plot \nati{I would drop this}
	\item result tables: only what supports the main message in the text, everything we have in the appendix \nati{I think this is done now}
	\item Unify vocabulary. Sampling, discretization, or pixelization of the sphere? Signal, maps, functions. Irregular, uneven. Coarsening, down-sampling.
	\item check English vs American English
	\item unify enumerations. I like (i), (ii), etc.
	\item add \citet{bruna2013gnn} in equivariance? They were the first to do a spherical CNN with graphs. Graph is built from a uniform random sampling of the sphere. \nati{Where do you want to add them?}
	\item figure placements \nati{Good according to me}
	\item do the experiments on the icosahedral grid with the pooling as defined in the paper \nati{I guess we are not doing that.}
	\item put all the code (learning experiments from Frédérick and equivariance experiments from Martino) in a common reproducible git repository to be linked from the paper
	\item update pygsp and merge sphere branch
	\item check that NN architectures and hyper-params are correctly reported
	\item keep NN architecture and hyper-params in the main text? Move the paragraph to appendix if not enough space. \nati{I think this does not apply anymore}
	%\item shall we still site adam and batch norm? no, mainstream enough
	\item check results for ModelNet40 and integrate in text \nati{I would drop this}
	\item Check that HEALPix is introduced in the introduction
	\item heuristic used to set the kernel width in v1. Add values to \figref{kernel_widths} for comparison.  \nati{Bit syre what you mean here...}
% 	\item check experiments section [Frédérick]: all the results numbers and NN + training details
	\item compute the invariance error of the whole NNs (before and after training, invariance can be learned) \nati{I guess we are not doing that}
	\item add it with equivariance error of the convolution to \tabref{cosmo}
	\item insert \citet{jiang2019sphericalcnn} in intro: Need a global coordinate system (ok for planets, not projections like cosmo)
\end{itemize}
}

\todo{
rebuttal:
\begin{itemize}
    \item answer reviewers and commenters [mdeff \& nath]
    \item update the proof [nath \& martino]
    \item better link between the proof and equivarian
    \item publish the code and link it here
	\item add somewhere: exploit symmetries to reduce sample cost
	\item proposition 1 -> corollary 3.1?
	\item \citet{Mudigonda} used Integrated Water Vapor (IWV) only. That most probably is the same as our TMQ, which is most probably the most informative feature. TODO: run ours with TMQ alone.
\end{itemize}
}

@@

\begin{abstract}
% We have to submit soon... The last sentence is a bit disconnected. Yep, better... Let submit... It is time.... Submit Submit Submit Submit 2 minutes... DONE!!!!!
Designing a convolution for a spherical neural network requires a delicate tradeoff between efficiency and rotation equivariance.
% exactitude with respect to equivariance.
DeepSphere, a method based on a graph representation of the discretized sphere, strikes a controllable balance between these two desiderata.
% Say something here about isotropy?
This contribution is twofold.
First, we study both theoretically and empirically how equivariance is affected by the underlying graph with respect to the number of pixels and neighbors.
Second, we evaluate DeepSphere on relevant problems.
Experiments show state-of-the-art performance and demonstrates the efficiency and flexibility of this formulation.
Perhaps surprisingly, comparison with previous work suggests that anisotropic filters might be an unnecessary price to pay.
%Say something about speed here... Not sure what?
% memory, computations, implementation complexity
\end{abstract}

>>>>

\newcommand{\fix}{\marginpar{FIX}}
\newcommand{\new}{\marginpar{NEW}}
\newcommand{\todo}[1]{{\color[rgb]{.6,.1,.6}{#1}}}
\newcommand{\nati}[1]{{\color[rgb]{.3,.5,.9}{#1}}}
\newcommand{\mart}[1]{{\color[rgb]{.9,.5,.3}{#1}}}
\newcommand{\mdeff}[1]{{\color[rgb]{.3,.8,.3}{#1}}}

@@

story: there are tradeoffs when designing a spherical CNN $\Rightarrow$ DS strikes a controllable balance between efficiency / cost and exactitude / equivariance
\begin{itemize}
	\item method development: tool that solve a need (balance btw the desiderata: equiv vs cost)
	\item research question: anisotropy (highlight from the start or leave it as a dangling question at the end)
\end{itemize}

contributions:
\begin{itemize}
	\item theory $\Rightarrow$ convergence (better graph)
	\item experiments on relevant problems (not spherical MNIST) $\Rightarrow$ check the desiderata
	\item surprising: anisotropy doesn't seem useful
\end{itemize}

\todo{
TODO:
\begin{itemize}
	\item PSD of climate data: how does it compare to cosmo and 3D objects? Climate data on spectrum plot. \nati{I would drop this}
	\item Unify vocabulary. Sampling, discretization, or pixelization of the sphere? Signal, maps, fields, functions. Irregular, uneven. Coarsening, down-sampling. Sample, vertex, node, pixel, point.
	\item check English vs American English
	\item Explain heuristic used to set the kernel width in v1. Add values to \figref{kernel_widths} for comparison. \nati{Not sure what you mean here.}
	\item put all the code (learning experiments from Frédérick and equivariance experiments from Martino) in a common reproducible git repository to be linked from the paper
	\item update pygsp and merge sphere branch
	\item Compute the invariance error of the whole NNs (before and after training, invariance can be learned). Add it with equivariance error of the convolution to \tabref{cosmo}. \nati{I guess we are not doing that}
	\item insert \citet{jiang2019sphericalcnn} in intro: Need a global coordinate system (ok for planets, not projections like cosmo)
	\item mention that \citep{esteves2018sphericalcnn} and \citep{cohen2018sphericalcnn} computed equivariance error
\end{itemize}
}

\todo{
rebuttal:
\begin{itemize}
    \item answer commenter
	\item add somewhere (intro?): exploit symmetries to reduce sample cost $\Rightarrow$ we don't discuss symmetries much
	\item \citet{mudigonda2017climateevents} use Integrated Water Vapor (IWV) only. That most probably is the same as our TMQ, which is most probably the most informative feature. TODO: run ours with TMQ alone.
	\item Show the three samplings in a figure?
	\item better abstract (Friday's talk abstract?)
	\item conclusion: less speculation?
	\item check feedback from ICLR'20 LTS2 reading group
	\item \mdeff{check my Telegram notes}
\end{itemize}
}

\todo{
last pass:
\begin{itemize}
	\item figure placement
	\item check footnotes
\end{itemize}
}

\todo{
Not done:
\begin{itemize}
	\item Do the experiments on the icosahedral grid with the pooling as defined in the paper (i.e., not Jiang's specialty of taking the value of a pre-chosen sub-pixel). \nati{I guess we are not doing that.} \mdeff{I'm not sure what is the state of this, and Frédérick is not with us anymore. It's quite minor.}
	\item Check results for ModelNet40 and integrate in text. \nati{I would drop this.} \mdeff{Yeah, those results are not mature enough.}
	\item Add \citet{bruna2013gnn} in equivariance? They were the first to do a spherical CNN with graphs. Graph is built from a uniform random sampling of the sphere. \nati{Where do you want to add them?} \mdeff{They don't write how their Laplacian was built. Also, they only did MNIST on the sphere...}
\end{itemize}
}

@@

\begin{abstract}
Designing a convolution for a spherical neural network requires a delicate tradeoff between efficiency and rotation equivariance.
% exactitude with respect to equivariance.
DeepSphere, a method based on a graph representation of the discretized sphere, strikes a controllable balance between these two desiderata.
% Say something here about isotropy?
This contribution is twofold.
First, we study both theoretically and empirically how equivariance is affected by the underlying graph with respect to the number of pixels and neighbors.
Second, we evaluate DeepSphere on relevant problems.
Experiments show state-of-the-art performance and demonstrates the efficiency and flexibility of this formulation.
Perhaps surprisingly, comparison with previous work suggests that anisotropic filters might be an unnecessary price to pay.
%Say something about speed here... Not sure what?
% memory, computations, implementation complexity
\end{abstract}
